\documentclass[a4paper]{amsart}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{cite}
\usepackage{amssymb,amsthm,amsmath,mathrsfs,amsfonts}
\usepackage{fancyhdr}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{amssymb, amsmath,amsthm,xcolor,bm,color,tikz,euscript}
\usepackage{xcolor,bm,tikz,euscript,sansmath,mathtools}
\usetikzlibrary{3d,calc}
\usetikzlibrary{positioning,matrix,arrows,decorations.pathmorphing}
\usepackage{amssymb,amsthm,amsmath,mathrsfs}
\usepackage{graphicx,enumerate, microtype}
\usepackage{xcolor,bm,color,tikz,euscript,sansmath}
\usepackage{tikz-cd}
\usepackage{subfig}

\usepackage[all]{xy}

\usepackage{hyperref}
\usepackage{url, hypcap}
\definecolor{darkblue}{RGB}{0,0,160}
\hypersetup{
colorlinks,%
citecolor=darkblue,%
filecolor=black,%
linkcolor=darkblue,%
urlcolor=darkblue
}

\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\tikzstyle{invisivertex} = [black, shape=rectangle, minimum size=0pt, inner sep=3pt]
\tikzstyle{circledvertex} = [violet!80, draw, shape=circle, minimum size=0pt, inner sep=3pt]
\tikzstyle{dot} = [black, fill, shape=circle, minimum size=3pt, inner sep=2pt]
\tikzstyle{opendot} = [draw, black, shape=circle, minimum size=6pt, inner sep=1pt]
\tikzstyle{edgelabel} = [magenta, shape=circle, minimum size=6pt, inner sep=1pt]

\usepackage[colorinlistoftodos]{todonotes}
\setlength{\marginparwidth}{2cm}
\newcommand{\galen}[1]{\todo[size=\tiny,color=blue!30]{#1 --G.}}
\newcommand{\raul}[1]{\todo[color=green!10,inline]{Raul: #1}}
\newcommand{\ben}[1]{\todo[size=\tiny,color=violet!30]{#1 --Ben}}


\usepackage{cleveref}
%
% \usepackage{array}
% \usepackage{cite}
% \usepackage{amssymb,amsthm,amsmath,mathrsfs,amsfonts}
% \usepackage{fancyhdr,color}
% \usepackage{amsmath,amssymb,amsthm,graphicx,enumerate, fancyhdr, microtype}
% \usepackage{amssymb, amsmath,amsthm,xcolor,bm,hyperref,color,tikz,euscript}
% \usepackage{xcolor,bm,hyperref,color,tikz,euscript,sansmath,ytableau, mathtools}
% \usetikzlibrary{3d}
% \usetikzlibrary{positioning,matrix,arrows,decorations.pathmorphing}
% \usepackage{amssymb,amsthm,amsmath,mathrsfs}
% \usepackage{fancyhdr,color}
% \usepackage{graphicx,enumerate, fancyhdr, microtype}
% \usepackage{xcolor,bm,color,tikz,euscript,sansmath,ytableau}
% \usepackage{tikz-cd}
% \usepackage{subfig}
%
% \usepackage{cleveref}
% \usepackage{todonotes}

\usepackage[all]{xy}

%\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{bbm}

% Abbreviations:

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\cL}{\mathcal{L}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cpI}{p\mathcal{I}}
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\GL}{\mathbf{GL}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bw}{\mathrm{bw}}
\newcommand{\tw}{\mathrm{tw}}

\newcommand{\init}{\mathrm{in}}
\newcommand{\LT}{\init}


% \newcommand{\RR}{\mathbf{R}}

\newcommand{\aaa}{\mathbf{a}}
\newcommand{\bbb}{\mathbf{b}}
\newcommand{\ccc}{\mathbf{c}}
\newcommand{\ddd}{\mathbf{d}}

\newcommand{\C}{\mathbb{C}}
\newcommand{\Tr}{{\sf Tr}}
\newcommand{\Gr}{{\sf Gr}}
\newcommand{\Var}{{\sf V}}
\newcommand{\Ideal}{{\sf I}}
\newcommand{\Mat}{{\sf Mat}}
\newcommand{\rank}{{\sf rank}}
\newcommand{\cols}{{\sf cols}}
\newcommand{\sqf}{\mathsf{sf}}
\newcommand{\Hilb}{{\sf Hilb}}
\newcommand{\minors}{{\sf minors}}
\newcommand{\len}{\ell}

\newcommand{\vv}{\mathsf{v}}
\newcommand{\vw}{\mathsf{w}}
\newcommand{\vj}{\mathsf{j}}
\newcommand{\vx}{\mathsf{x}}
\newcommand{\vy}{\mathsf{y}}
\newcommand{\vz}{\mathsf{z}}
\newcommand{\va}{\mathsf{a}}

\DeclareMathOperator{\spn}{span}

\newcommand{\Dfn}[1]{\emph{\bfseries #1}}


% stats
\newcommand{\E}{\mathbb{E}}

%
% Math environment setup:
%
\newtheorem{lemma}{Lemma}
\newtheorem{claim}[lemma]{Claim}
\newtheorem{proposition}[lemma]{Proposition}
\newtheorem{thm}[lemma]{Theorem}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{cor}[lemma]{Corollary}
\newtheorem{conjecture}[lemma]{Conjecture}
\newtheorem{guess}[lemma]{Guess}

% Definition:
\theoremstyle{definition}
\newtheorem{definition}[lemma]{Definition}
\newtheorem{problem}[lemma]{Problem}

\theoremstyle{remark}
\newtheorem{to do}[lemma]{To Do}
\newtheorem{observation}[lemma]{Observation}

\newtheorem{remark}[lemma]{Remark}
\newtheorem{note}[lemma]{Note}
\newtheorem{question}[lemma]{Question}

\theoremstyle{remark}
\newtheorem{example}[lemma]{Example}

\title{Distribution parameter inference with minimal oracle access}
\date{\today}
\author{Raul Penaguiao}

\begin{document}



\begin{abstract}
In this paper we explore a problem with corrupted databases and error correction.
An exploratory essay on inferring properties of a distribution by sampling.
\end{abstract}

\maketitle




\section{Introduction}

When creating or working with structured data, data sanitization is fundamental for the correct inference of properties of interest.
However, that may not be readily available, due to costs or time constraints, and we must expediently assess variables of interest in the database through sampling.
In this essay we propose to do exactly that, via two different methods.

We will now describe the theoretical problem.
Fix a parameter $p$.
There are two probability distributions $\mu_Y$ and $\mu_Z$ that are unknown, of which the following mixing $\mu_X$ is created:
Let $I \sim \mathrm{Bernoulli}(p)$, then $X = I \times Y + (1 - I) \times Z$.
The distribution $\mu_X$ is known.
We will interpret $Z$ to describe erroneous database entries and will have a different distribution from $Y$, the target data to be studied.

We have access to an oracle $\mathcal O$ that, given a sampled data from $\mu_X$, determines whether this data came from the distribution $\mu_Z$ or $\mu_Y$.
In this way, and by sampling and accessing the oracle an unlimited amount of times, we are able to assess the distributions of $\mu_Y, \mu_Z$.
The following problem tries to do this in the most economical way.


\begin{problem}
Find a $95 \%$ confidence interval for the expected value of the distribution $\mu_Y$ with a minimal number of access to the oracle.
\end{problem}


This is an exploratory essay on inferring properties of a distribution by sampling.


\section{Methods proposed}


\subsection{Bucket method}

We will find the distribution of $Z$ and $Y$ by sampling.

\subsection{Weighted sampling}


Our goal is to estimate $\E [ Y ]$ via $\E [ X ] = p \E[Y] + (1-p) \E[Z]$.

\bibliographystyle{plain}
\bibliography{bibliog}


\end{document}
